---
title: "Marking open-ended questions wuth Topic modelling and LDA"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Text analysis/topic modelling
* Open-ended questions questions are more eficient/complete assessments.
* But are also harder to mark.
    + we want to use here text/topic analyis/minning...
* Text in `R` means a object `string`
    + so we are doing string manipulation
* *Moodle*, R/exams and open-ended questions...


## Text processing and analysis
* String manipulation 
* general pattern analysis 
* key terms 
* grouping ansewrs

### String manipulation
```{r}
# answers <- read.csv2("respostas_IC_conclusao-interpretacao.xml").
# head(answers)
```

### word cloud 
*for an overview on the answers

### *must have* words 
* to get marks for key words/sentences... and lose marks as well...

### Latent Dirichlet Allocation (dicriminat analysis...) to mark `string` text answers
* to group students by similarities... to check for copying, cheating, ...



https://rpubs.com/Argaadya/topic_lda

https://rstudio-pubs-static.s3.amazonaws.com/100936_ae4251bba3da438bbfb870d4b9431f04.html


papers

https://scholar.harvard.edu/files/dtingley/files/topicmodelsopenendedexperiments.pdf

https://www.tandfonline.com/doi/full/10.1080/2573234X.2019.1590131

file:///C:/Users/Markus/Downloads/information-11-00550.pdf

### References
* An Introduction to Text Processing and Analysis with R
    + https://m-clark.github.io/text-analysis-with-R/string-theory.html#basic-text-functionality
    
* Text Processing in R
    + http://www.mjdenny.com/Text_Processing_In_R.html